\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web

### 2020-03-16 revision3_2581/paper.tex
Rearranged data sources to match Figure 1
Added SRS to the article
Update year for online references

\author{Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And 
        Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

\Plainauthor{Eduard Sz\"ocs, Ralf B. Sch\"afer}

@@

\begin{description}
\item[NIH Chemical Identifier Resolver (CIR)]{\citep{cir} A web
    service that converts from and to various chemical identifiers. The database holds millions of identifier combinations.}
\item[Chemical Translation Service (CTS)]{
  \citep{Wohlgemuth_Haldiya_Willighagen_Kind_Fiehn_2010} A web
    service that converts from and to various chemical identifiers.}
\item[ETOX]{\citep{etox} Information System Ecotoxicology and
    Environmental Quality Targets by the German Federal Environmental
    Agency. Provides basic identifiers, synonyms, ecotoxicological
    data for over 64,000 entries and quality targets for different countries.}
\item[PAN Pesticide Database]{ \citep{pan} Information on pesticides --
    provides basic identifiers, ecotoxicological data, chemical
    properties, uses and regulatory status for 6,500 pesticides.}
\item[PubChem]{\citep{Kim_2016} PubChem is a public repository for
    information on more than 250 million chemical substances, providing identifiers,
    properties and synonyms. We use an interface to the PUG-REST web
    service \citep{Kim_Thiessen_Bolton_Bryant_2015}.}
\item[Wikidata]{\citep{wiki} Wikipedia contains information for over
    210,000 chemicals
    \citep{Ertl_Patiny_Sander_Rufener_Zasso_2015}. Currently
    \pkg{webchem} can only query chemical identifiers.}
\item[Compendium of Pesticide Common Names]{\citep{wood} The
    compendium provides information on pesticide common names,
    identifiers and classification. The compendium contains more than 1800 active ingredients and more than 350 ester and salt derivatives. }
\item[ChemID\emph{plus}]{\citep{Tomasulo_2002} is a large web-based
    database provided by the National Library of Medicine. It contains
    identifiers, synonyms, toxicological data and chemical
    properties for over 420,000 records.}
\item[ChemSpider]{\citep{pence_chemspider:_2010} is a free chemical
    structure database providing access to over 67 million
    structures from hundreds of data sources. It provides identifiers, properties and can also be
    used to convert identifiers.}
\item[OPSIN]{\citep{Lowe_Corbett_Murray-Rust_Glen_2011} The Open
    Parser for Systematic IUPAC nomenclature is a chemical name
    interpreter and provides InChI and SMILES identifiers.}
\item[Flavornet]{\citep{flavornet} Flavornet is a compilation of 738 aroma compounds found in human odor space.}
\item[NIST]{\citep{nist} The NIST Chemistry WebBook provides access to data compiled and distributed by NIST under the Standard Reference Data Program. The WebBook provides chemical and physical property data on over 40,000 compounds.}
\item[ChEBI]{\citep{chebi} Chemical Entities of Biological Interest (ChEBI) is a freely available dictionary of molecular entities focused on "small" chemical compounds. The database contains more than 56,000 compounds.}

>>>>

\author{Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And
	Tam\'as Stirling\\Independent Developer \And
        Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

\Plainauthor{Eduard Sz\"ocs, Tam\'as Stirling, Ralf B. Sch\"afer}

@@

\begin{description}
\item[NIH Chemical Identifier Resolver (CIR)]{\citep{cir} A web
    service that converts from and to various chemical identifiers. The database holds millions of identifier combinations.}
\item[ChemSpider]{\citep{pence_chemspider:_2010} is a free chemical
	structure database providing access to over 67 million
	structures from hundreds of data sources. It provides identifiers, properties and can also be
	used to convert identifiers.}
\item[Chemical Translation Service (CTS)]{
  \citep{Wohlgemuth_Haldiya_Willighagen_Kind_Fiehn_2010} A web
    service that converts from and to various chemical identifiers.}
\item[ETOX]{\citep{etox} Information System Ecotoxicology and
    Environmental Quality Targets by the German Federal Environmental
    Agency. Provides basic identifiers, synonyms, ecotoxicological
    data for over 64,000 entries and quality targets for different countries.}
\item[ChemID\emph{plus}]{\citep{Tomasulo_2002} is a large web-based
	database provided by the National Library of Medicine. It contains
	identifiers, synonyms, toxicological data and chemical
	properties for over 420,000 records.}
\item[OPSIN]{\citep{Lowe_Corbett_Murray-Rust_Glen_2011} The Open
	Parser for Systematic IUPAC nomenclature is a chemical name
	interpreter and provides InChI and SMILES identifiers.}
\item[Compendium of Pesticide Common Names]{\citep{wood} The
	compendium provides information on pesticide common names,
	identifiers and classification. The compendium contains more than 1800 active ingredients and more than 350 ester and salt derivatives. }
\item[Wikidata]{\citep{wiki} Wikipedia contains information for over
	210,000 chemicals
	\citep{Ertl_Patiny_Sander_Rufener_Zasso_2015}. Currently
	\pkg{webchem} can only query chemical identifiers.}
\item[PubChem]{\citep{Kim_2016} PubChem is a public repository for
    information on more than 250 million chemical substances, providing identifiers,
    properties and synonyms. We use an interface to the PUG-REST web
    service \citep{Kim_Thiessen_Bolton_Bryant_2015}.}
\item[PAN Pesticide Database]{ \citep{pan} Information on pesticides --
	provides basic identifiers, ecotoxicological data, chemical
	properties, uses and regulatory status for 6,500 pesticides.}
\item[Flavornet]{\citep{flavornet} Flavornet is a compilation of 738 aroma compounds found in human odor space.}
\item[NIST]{\citep{nist} The NIST Chemistry WebBook provides access to data compiled and distributed by NIST under the Standard Reference Data Program. The WebBook provides chemical and physical property data on over 40,000 compounds.}
\item[ChEBI]{\citep{chebi} Chemical Entities of Biological Interest (ChEBI) is a freely available dictionary of molecular entities focused on "small" chemical compounds. The database contains more than 56,000 compounds.}
\item[SRS]{\citep{srs} Substance Registry Services is the US EPA central system for information about substances that are tracked or regulated by EPA or other sources.}
